\Large Inferential Analysis of the Supreme Court Citation Network

### 2018-02-19 Tex/paper.tex

 \section{Empirical Analysis}
Our three data sources for this study include the SCDB, Martin-Quinn scores, and Supreme Court citation data provided by Courtlistener ?cite. We limit the Supreme Court terms included in our analysis to those that are covered by all three of these data source (1937--2015).  The Supreme Court citation network from $1937 - 2015$ consists of $9,841$ cases. The breakdown of the data by the Court's Chief Justice is presented in Table \ref{tab:chiefs}. The network has a total of $110,742$ ties. The number of triangles in the network is $246,134$. The in- and outdegree distributions (i.e., the distributions of the number of citations sent and received by cases, respectively), are visualized in figures \ref{indegree_dist} and \ref{outdegree_dist}. The maximum indegree is $228$ and the maximum outdegree is $162$.

>>>>

 \section{Empirical Analysis}
Our three data sources for this study include the SCDB, Martin-Quinn scores, and Supreme Court citation data provided by Courtlistener ?cite. We limit the Supreme Court terms included in our analysis to those that are covered by all three of these data source (1937--2015).  The Supreme Court citation network from $1937 - 2015$ consists of $9,841$ cases. The breakdown of the data by the Court's Chief Justice is presented in Table \ref{tab:chiefs}. The network has a total of $110,742$ ties. The number of triangles in the network is $246,134$. The in- and outdegree distributions (i.e., the distributions of the number of citations sent and received by cases, respectively), are visualized in Figure \ref{degree_dist}. The maximum indegree is $228$ and the maximum outdegree is $162$.
